---
title: "Whatever I want to call it (gapminder) :)"
author: "T. Griffin"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
    code_folding: hide
    
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the first line of this document. Include information about the purpose of this document.

# READING IN GAPMINDER DATA (the hashtag creates a header)

```{r Reading-in-data}
gapminder_df <- read.csv("Data/gapminder_data.csv")


```

## A smaller header (more hashtags make the header smaller)

### A smallest header

#### a header to the \^-4

List:

-   Item 1
-   Item 2

Another list:

-   Hyphen list
-   hyphen 2

Numbered list:

1.  N1
2.  N2 \*sub list
3.  N3

We can make text **bold with two asterisks** or *italic with one*

We can also insert greek letters $\mu$ $\Delta$

We can make [hyperlinks](https://pad.carpentries.org/Spring2024-BIOMI6300)

# Calculating summary statistics

```{r calculating-median-pop, echo= FALSE}

med_pop <- median(gapminder_df$pop)

num_obs <- nrow(gapminder_df)
```

Over `r num_obs` observations, the median population was `r round(med_pop/10e6, 3)` million people.

#Plotting life expectancy over the years

```{r line-graph, eval = FALSE, warning= FALSE}
#library(ggplot2)

ggplot(gapminder_df, aes(x = year, y = lifeExp, group = country, color = continent)) +
  scale_y_log10() +
  geom_line() +
  scale_x_continuous(limits = c(1997, 2007))
#geom_smooth adds a line of best fit; it does not make a line graph. geom_line does that :)
```

#Plotting Population Distribution `{r histogram, message = FALSE, fig.width= 10} #fig width is in inches #making a histogram ggplot(gapminder_df, aes(x = pop)) + geom_histogram()`

a shown above, the median population was 7023596

#insert table

```{r}
```


and we add some new lines b/c of git